\documentclass[11pt,a4paper,sans]{moderncv}
% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{black}


\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}
%% Character encoding
\usepackage[utf8]{inputenc}
%% Adjust the page margins
\usepackage[scale=0.75]{geometry}
%% Personal data
\firstname{Luc}
\familyname{Geurts}
\address{Orléans, Centre-Val de Loire, France}
%\mobile{}
\email{lgeurts@protonmail.com}
\social[github]{lgeurts}
\social[linkedin]{www.linkedin.com/in/lucgeurts}

\begin{document}

\makecvtitle

\section{Summary}
{
  A highly motivated Ops. Team Lead / Sr. Platforms Engineer with 
  over 15 years of hands-on and 4+ years of leadership experience. 
  Specializing in Microsoft Cloud Services, Windows Server (with 
  sub-specialties in clustering, performance tracing and analysis,
  virtualization, crash dump debugging), and some skills in Amazon
  Web Services (AWS), Software Engineering & Linux OS.
}
\section{Experience}
\cventry{2017}{DevOps|Cloud Platforms Engineer}{Self-Employed}{France}
{
  Some of my main ongoing missions:
• Freelance contractor at a medium sized travel company (FR HQ, subs in the UK, NL, BE). 
  I help them build/scale a functional service (Website, APIs, mobile apps), migrate to Amazon Cloud 
  i.e. AWS, manage the new automation infrastructure, as well as recruit a new team of engineers.
• Maintain a mixed Windows/Linux environment at a school for at-risk middle/high school children (on a voluntary basis). 
  Currently implementing OMI CIM server, DSC, and upgrading +800 client devices.
• Coach & tech advisor for two early stage startups.
}
\cventry{2012--2017}{Premier Field Engineer Platforms}{Microsoft}{Germany}
{
  The bullet point description of my job?
• Assist MCS (Microsoft Consulting Services) by providing technical 
  support in developing 'Tailored to Fit' solutions for Premier 
  customers.
• Deliver proactive on-site Windows Platforms DSE services in the 
  EMEA region.
• Work on technically complex, politically hot customer issues, and maintain case ownership until resolved.
• Create different types of offerings such as workshops and chalk talks.
• Mentor new hires; helping them adjust and discover more about the organization and culture as well as enhancing their technical expertise.
• Moderate and participate in select forums and newsgroups.
}
\cventry{2011--2012}{Escalation Engineer}{Dell}{Ireland}
{
• Managed Tier 3 escalations and subcases, addressing and resolving break-fix incidents.
• Delivered high quality fixes for Dell KACE, vRanger and Foglight end-to-end software.
}
\cventry{2011--2011}{Support Escalation Engineer}{Hewlett-Packard}{Ireland}
{
• Tracked product support cases and executed post-mortem processes on closing critical issues.
• Wrote technical articles and white papers on multiple products for the external VKB; focusing on symptoms, root causes, and resolutions.
• Engaged in Early Assist for key products in order to maintain product knowledge.
}
\cventry{2006--2010}{Owner}{GEURTS-IT B.V.}{Netherlands}
{
• Performed all responsibilities as a self-employed entrepreneur.
• Worked as a contractor at various projects.
}

\section{Accreditations}
\cvlistdoubleitem{Kernel Debugging for PFE's Workshop} {CSS Data Gathering Workshop}

\section{Publications}
\cvlistdoubleitem{Kernel Debugging for PFE's Workshop} {CSS Data Gathering Workshop}


\cvlistdoubleitem{Unix tools (Git, Vim, Bash)} {Amazon Web Services}
\cvlistdoubleitem{Java, Groovy, Scala} {SQL}
\cvlistdoubleitem{Bash} {C++}
\cvlistdoubleitem{Python} {Haskell}

\section{Education}
\cventry{1987--1989}{Telecommunications & Electromechanical Engineering}{Military School}{Doornik, Belgium}{}{}
\cvlistdoubleitem{Network Security}                 {Data Structures and Databases}
\cvlistdoubleitem{Programming Languages and Design} {Computer Architecture}
\cvlistdoubleitem{Cloud Computing}                  {Operating Systems}
\cvlistdoubleitem{Analysis of Algorithms}           {Human Computer Interaction}
\end{document}
