% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/lgeurts/resume/
%
% Author:
% Luc Geurts (Flous)
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: expérience
\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Now}           {Lead Project Engineer}{ITIS Projects B.V.}{Netherlands}
    {March 2019}    {
                      \begin{itemize}                        
                        \item Agile SecOps at the Dutch Ministry of Justice and Safety. We focus on monitoring and assessing risks thru automated pentesting and running product workshops for members of Police/KMAR units and Rijksrecherche.  

                        \item Sub-Contractor at  Huisman Equipment:
                        \newline Introduce, design, build private on-site Git and cloud based VSTS repositories under Azure DevOps. Combining these two options gave us the ability to build our change management plan by simply linking  the work items, bugs and code changes together under any given User Story, regardless if data was located in the vendor's tenant or kept inside the company firewall.
                        \linebreak Act as the site's main Technical Editor publishing step by step tutorials, infrastructural designs, later on switching to more generic content like policies and a new global IT governance framework.
                        \linebreak Manage projects. As example rolling out a BeyondTrust PAM solution at 5 regions and +200 subscribed vessels.
                        \linebreak Prep \& run classroom training sessions for NOC engineers and Helpdesk staff.      
                      \end{itemize}
                    }
                    {Oracle Linux, Microsoft Entra ID, Active Directory, Kanban, Scrum, BeyondTrust, Git, PowerShell, Markdown}
  \emptySeparator
  \experience
    {Now}           {Co-Founder | Tech Lead | Engineering Consultant}{Flouze EURL}{France}
    {September 2017}{
                      \begin{itemize}
                        \item Interim Technology Lead at a leading travel and tourism group: 
                        \newline After migrating departmental resources to AWS, my team is occupied with maintaining functional services (websites, APIs, mobile apps) and automating EC2 provisioning through Ansible Tower.                           

                        \item Manage the migration of a financial apps cluster at Le Crédit Lyonnais.                       

                        \item Maintain a predominantly Microsoft \& Apple based infrastructure at a high school for at-risk children. This is a voluntary job (FACE aka Fondation Agir Contre l'Exclusion).

                        \item Coach \& Tech Advisor for two startups (remote workspaces and financial modeling).           
                      \end{itemize}
                    }
                    {AWS, Amazon Linux 2, Jira, Confluence, Ansible, Amazon LightSail, Docker, Amazon Workspaces, Active Directory, Softerra Adaxes, LibreOffice, Gherkin, Git, Bash, PowerShell, JSON, YAML}
  \emptySeparator
  \experience 
    {September 2017}{Premier Field Engineer}{Microsoft GmbH}{Germany}
    {March 2012}    {
                      \begin{itemize}
                        \item Assist MCS (Microsoft Consulting Services) by providing technical support in developing 'Tailored to Fit' solutions for Premier customers like for example Finanz Informatik, PWC, and Deutsche Bahn.

                        \item Create/teach different types of offerings such as Workshops, Chalk \& Talks.  
                        
                        \item Deliver proactive on-site Windows Platforms DSE services in the DACH region (70\%).                   
 
                        \item Participate in on-call shifts, CritSits, and Health Checks (transactional, Europe, 30\%).    

                        \item Mentor new hires; helping them adjust and discover more about our organization and its culture, as well as enhancing their technical expertise.
                      \end{itemize}
                    }
                    {Microsoft Entra ID, Hybrid Identity, Active Directory, VitalSigns Performance Monitoring, Microsoft HPC, PKI, Hyper-V, Winternals, Intune MDM/MAM, DFS, VDI, RDS, DSC, MDT, WinDbg, Netmon, PowerShell}
  \emptySeparator
  \experience
  {February 2012}   {Escalation Engineer}{Dell Technologies Ltd}{Ireland}
  {July 2011}       {
                      \begin{itemize}
                        \item Managing Tier 3 escalations and subcases; addressing high priority break-fix incidents.                            
                      \end{itemize}
                    }
                    {KACE, vRanger, Foglight, Microsoft Windows, VMware, WinDbg, PowerShell, Wireshark}
  \emptySeparator
  \experience
  {July 2011}       {Support Escalation Engineer}{Hewlett-Packard Ltd. for Microsoft CSS}{Ireland}
  {February 2011}   {                    
                      \begin{itemize}
                        \item PSS provides pay-per-incident support for IT experts and businesses. More often than not, many of these support cases with their symptoms, root causes and resolutions, will land as a white paper in the external VKB (Microsoft portal for partners) or TechNet. I was working in the Windows Server team.                                       
                      \end{itemize}
                    }
                    {Active Directory, Microsoft Windows, Exchange Server, WinDbg, Netmon, Xperf}
  \emptySeparator   
  \consultantexperience
  {December 2010}   {CEO, Consultant}{GEURTS-IT B.V.}{Netherlands}
  {February 2006}   {Technical Lead, Sr. Engineer}{Gemeente Dordrecht, Eneco Energie, DAF Trucks, SWIFT, KPN Telecom}
                    {
                      \begin{itemize}
                        \item In chronological order:
                        \newline Architecting the layout of a regional datacenter/scripting VMware ESX acceptance tests for certification purposes.
                        \linebreak Spearheading the migration of Windows \& Linux BC/OD financial clusters and services to a 3rd party datacenter.
                        \linebreak Driving the integration of a vendor's application landscape and infrastructure into the PACCAR holding.
                        \linebreak Designing the blueprint for a new Microsoft Operations Manager 2005 architecture, building a solid base of Microsoft SMS 2003 Management Packs, and providing ad-hoc training to operational staff.
                        \linebreak Upgrading a batch of 42 EOL OpalisRobot 4.0 automation systems to Opalis Integration Server 5.0.
                      \end{itemize}
                    }
                    {Lean, Autodesk BIM, Red Hat Enterprise Linux, VMware, OpalisRobot, MOM, SMS, ESX CLI, VBScript}
\end{experiences}